SciPy 1.0---Fundamental Algorithms for Scientific Computing in Python

### 2019-09-08 scipy-1.0/paper.tex
Introduced C libraries

Rounding out the top three languages in SciPy is C, which is also extremely
well-established over several decades\cite{Kernighan:1988:CPL:576122} of
scientific computing. The C libraries that we wrap in SciPy include
trlib\cite{doi:10.1080/10556788.2018.1449842}, % (iterative solving of the trust region problem),
SuperLU\cite{li05,superlu_ug99}, % (solution of large, sparse, nonsymmetric systems of linear equations),
Qhull\cite{Barber:1996:QAC:235815.235821}, and % (computational geometry)
Cephes\cite{cephes_netlib}. % (mathematics algorithms).

>>>>

Rounding out the top three languages in SciPy is C, which is also extremely
well-established over several decades\cite{Kernighan:1988:CPL:576122} of
scientific computing. The C libraries that we wrap in SciPy include
trlib\cite{doi:10.1080/10556788.2018.1449842} for optimization, % (iterative solving of the trust region problem),
SuperLU\cite{li05,superlu_ug99} for solving sparse linear systems, % (solution of large, sparse, nonsymmetric systems of linear equations),
Qhull\cite{Barber:1996:QAC:235815.235821} for computational geometry, and % (computational geometry)
Cephes\cite{cephes_netlib} for special functions. % (mathematics algorithms).
